\section{Minimum Dimension Code (Private Linear Computation)}

\begin{question}
  For given $D$ and $M$ and $L$.
  Design a code of length $n$ with minimum dinesion such that for any $D$-subset of coordinates $I$, there exists $L$ ``MDS-coded'' codewords $c_1,\dots,c_L$ of weight $D\le w(c_i)\le D+M$  such that $I\subset \supp(c_i)$ for all $i\in[L]$ and $(c_1)_I,\dots,(c_L)_I$ are linearly independent.
\end{question}

\begin{theorem}
  Dimension $\ceil{n/2}+1$  is achievable and is tight.

  In general, dimension 
  \begin{align}
  \ceil{(n-D-M)/(1+\ceil{M/D})}+1 
  \label{eq:opt?}
  \end{align}
  is achievable. 
  
  Anoosheh believes this is tight for $D\le M$.
  \label{}
\end{theorem}

\begin{enumerate}
  \item For $L=1$, $D\le M$, can you show the bound \eqref{eq:opt?}, at leats asymptotically?

  \item For $L=1$, $D>M$, the bound is $n-D-M$, which is $n-O(1)$. Can you get a construction with dimension $n-\omega(1)$? For $D=2,M=1$, this is possible over $\mathbb{F}_2$ by taking the Hamming code.
    What about other fields? What about arbitrary $D>M$? (In particular for $D$ arbitrary and $M=1$).

  \item $L$ larger.
\end{enumerate}


\section{$D>M$.}

\begin{theorem}
  Let $q$ be a prime power.
  For $D>M$, for infinitely many $n$, there exists a $\mathbb{F}_q$ linear code $C$ of dimension $n-\log_q(n/D)$ such that, for any set of coordinates $I\subset[n]$ of size $D$, there exists a codeword $c\in C$ of weight $D\le \wt(c)\le D+1$ such that $I\subset \supp(c)$.
  \label{}
\end{theorem}
\begin{proof}
  Let $r$ be a positive integer and let $n=(D+1)\cdot q^r$.
  Let $v_1,\dots,v_{q^r}$ be the vectors in $\mathbb{F}_q^r$.
  Consider the $r\times n$ parity-check matrix $H$ whose columns are $v_1,v_1,\dots,v_{q^r},v_{q^r}$, where each $v_i$ appears with multiplicity $D+1$.
  We claim the code with this parity check matrix has the desired property.

  First, the dimension of this code is $n-r = n-\log_q(n/D)$.

  Index the columns of $H$ by $\mathbb{F}_q^r\times [D]$.
  Consider any set of indices $I\subset \mathbb{F}_q^r\times [D]$.
  Then consider $\sum_{(i,d)\in I}^{} v_i$. This is equal to some vector $v_j\in\mathbb{F}_q^r$.
  Because we took every vector with multiplicity $D+1$, there is some index $d'$ such that $(j,d')\notin I$.
  Now take $c\in\mathbb{F}_q^n$ to be the vector where $c_i=1$ for $i\in I$ and $c_{(j,d')}=-1$, and $c_i=0$ elsewhere.
  You can check that
  \begin{align}
    H\cdot c = \left(\sum_{(i,d)\in I}^{} v_i\right)  - v_{(j,d')}.
    \label{}
  \end{align}
  so $c$ is a codeword. 
  By construction $c$ is supported on $I\cup \{(j,d')\}$, so $c$ is our desired codeword for $I$.
  This works for any $I$ so we are done.
  \ryl{You can replace $D+1$ with $D-1$ easily. Probably with some more work you can get an even better bound.}
\end{proof}
